\documentclass{article}

\usepackage[margin=1in]{geometry}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[none]{hyphenat}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Boston CV},
    pdfpagemode=FullScreen,
}
\usepackage{ifthen}

\urlstyle{same}

\setlist[itemize]{topsep=0.5\parskip, after=\vspace{0.5\baselineskip}}

\setcounter{secnumdepth}{0}
\setlist{nosep}
\setlength{\parindent}{0pt}

\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% \newcommand{\profileheading}[6]{
% \begin{parcolumns}[nofirstindent]{2}
% \end{parcolumns}
% \noindent\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{#1} & #2 \\
%   #3 & #4 \\
%   #5 & #6 \\
% \end{tabular*}
% }

\newcommand{\resumeSubheading}[5]{
\noindent\begin{minipage}{0.5\textwidth}
	\begin{flushleft}
	\textbf{#1}\\
	\textbf{#2}\\
	\end{flushleft}
\end{minipage}%
\hfill
\begin{minipage}{0.5\textwidth}
	\begin{flushright}
	#3\\
	#4\\
	\end{flushright}
\end{minipage}%
\newline
#5
%\leavevmode%\\%\newline
}

\newcommand{\award}[4]{
\begin{flushleft}
\textbf{#1}\\
#2 - #3\\
#4\\
\end{flushleft}
\leavevmode
}

\newcommand{\project}[3]{
\textbf{#1 (#2)} --- #3
}

% \newcommand{\resumeSubheading}[4]{
% \vspace{-1pt}\item[]
% % \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r}
% \begin{tabular*}{\textwidth}{l r}
%       \textbf{#1} & \textbf{#2} \\
%       \textit{#3} & \textit{#4} \\
%     \end{tabular*}\vspace{-5pt}
% }

\newcommand{\projectListing}[3]{
	\textbf{#1 (#2)} - #3
}

\begin{document}
\begin{flushleft}
\LARGE \textbf{Boston Lee} \\
\end{flushleft}

% Needed to make the table flush
\noindent\begin{minipage}{0.5\textwidth}
	\begin{flushleft}
	(970) 590-8726 \\
	boston.lee@gmail.com \\
	\end{flushleft}
\end{minipage}%
\hfill
\begin{minipage}{0.5\textwidth}
	\begin{flushright}
	\url{https://www.bostonlee.com/} \\
	\url{https://www.linkedin.com/in/boston-lee/} \\
	\end{flushright}
\end{minipage}%

\section{Education}

\begin{flushleft}
\textbf{Colorado State University, Honors Program}\\
Fort Collins, CO\\
August 2018 -- December 2021\\
BS Statistics (\textit{Summa Cum Laude}), BA Philosophy (\textit{Summa Cum Laude})\\
Cumulative GPA: 4.0
\end{flushleft}

\section{Languages and Tools}

\textbf{Languages}: Python, SQL, POSIX Shell, Bash, Java, Javascript, R

\textbf{Tools}: Git/GitHub/Bitbucket, AWS Services, Linux, UNIX Utilities, Snowflake

\section{Employment}

% Situation
% Task
% Action
% Response

\resumeSubheading{Data Engineer}{Proofpoint}{October 2022 - Present}{Remote}{
\begin{itemize}

	\item Architected internal package to process JSON payloads to machine learning inputs, using Pydantic
	\item Prototyped XGBoost-based classification model for classifying highly structured JSON payloads
	\item Maintained statistical machine learning model in production, managing model bug fixes, retraining, and deployment with AWS Sagemaker and AWS S3
	\item Added AWS Cloudwatch metrics to stateless classification service running on AWS Lambda using boto3, leading to greatly improved application visibility

\end{itemize}
}

\resumeSubheading{Data Engineer}{Ampt}{August 2021 - October 2022}{Fort Collins, CO}{
\begin{itemize}

	\item Managed migration from filesystem data storage to MySQL database storage on intermediate data servers, including overhaul of internal web service to accommodate a database backend. Roadmapped the develoment pipeline from initial prototyping to deployment.
	\item Prototyped, modeled, and implemented new MySQL database schema in collaboration with engineering requirements. Integrated database with existing data pipeline. 
	\item Built new ETL processes using Python, pandas, and SQLAlchemy.  Sped up ETL pipeline by \textasciitilde500\%, preventing latency and severe server downtime.
	\item Built REST API interface to MySQL database.
	\item Prototyped schemaless data storage in MongoDB, using pymongo. % CV-ONLY
	\item Architected upgraded Python package for custom parsing, allowing for deployment on edge devices. % CV-ONLY
	\item Created and managed multiple OpenVPN Ubuntu Linux servers hosted on DigitalOcean.
	\item Designed and implemented SQLite3 database to track OpenVPN metadata. % CV-ONLY
	\item Developed command-line tool in Bash for the management and automation of deployment of OpenVPN server and Certificate Authority. % CV-ONLY
\end{itemize}
}

\resumeSubheading{Data Analyst Intern}{Trinidad Benham}{March 2021 - August 2021}{Remote}{
\begin{itemize}

	\item Led creation of metadata database system for tracking multiple disparate databases and coordinating shared data views in a data warehouse.  Created the database design and scripted data insertion with Python.
	\item Scripted views for Snowflake data warehouse in SQL.
	\item Translated SSRS reports from legacy system using PostgreSQL, TSQL, Snowflake SQL.
	\item Managed driver configuration and workflow scripting for SSRS report translation % CV-ONLY

\end{itemize}
}

\resumeSubheading{Software Engineering Intern}{Ampt}{May 2020 - March 2021}{Fort Collins, CO}{
\begin{itemize}

	\item Independently developed a Python package using Pandas to parse a proprietary over-the-air (RF) network protocol. The package increased the speed of data processing by \textasciitilde40\%. Managed development, versioning, documentation, and deployment. 
	\item Developed and maintained an interactive graph dashboard for engineering and client use. Integrated the page into a Flask webserver, using Javascript as a frontend.
	\item Led initial testing of Zigbee wireless data collection, including research, scripting, and visualization. % CV-ONLY

\end{itemize}
}

\resumeSubheading{Teaching Assistant: Discrete Structures}{Colorado State University}{January 2020 - December 2020}{Fort Collins, CO}{ % CV-ONLY
\begin{itemize} % CV-ONLY

\item Led two weekly recitations, reinforcing class material.  Assisted students both in recitation and online. Graded course materials and exams. % CV-ONLY
\item Class topics included: Integer representations and properties, propositions, predicates, sets, functions, program proofs, induction, counting, complexity, and basic combinatorics. % CV-ONLY

\end{itemize} % CV-ONLY
} % CV-ONLY

\resumeSubheading{Research Assistant: Microbiology}{Colorado State University}{December 2018 - June 2019}{Fort Collins, CO}{ % CV-ONLY
\begin{itemize} % CV-ONLY
	\item Assisted with the execution of immunofluorescence and transfection experiments for kinetochore protein detection. % CV-ONLY
	\item Performed general lab support and maintained a sterile lab environment. % CV-ONLY
\end{itemize} % CV-ONLY
} % CV-ONLY

\resumeSubheading{Martial Arts Instructor}{International Black Belt Academy}{March 2018 - August 2018}{Fort Collins, CO}{ % CV-ONLY
\begin{itemize} % CV-ONLY
	\item Led youth camps, which involved full supervision of large % CV-ONLY
		groups of children. Constructed martial arts-based curriculum for children of % CV-ONLY
		all ages. % CV-ONLY
	\item Led youth karate instruction classes % CV-ONLY
	\item Developed curriculum for youth karate instruction at the appropriate level % CV-ONLY
	\item Led and assisted with planning and teaching adult karate instruction classes % CV-ONLY
	\item Led and assisted with planning and teaching adult kickboxing classes % CV-ONLY
	\item Assisted in teaching a women's self defense course % CV-ONLY
\end{itemize} % CV-ONLY
} % CV-ONLY

% \resumeSubheading{Test}{Test}{Test}{Test}


\section{Projects} % CV-ONLY
 % CV-ONLY
\project{Honors Thesis}{F 2021}{The Relationship Between Financial Stress and Mental Health in the US}\\ % CV-ONLY
\project{Class Project}{F 2021}{Time-series boostrapping for solar cell output using NREL data}\\ % CV-ONLY
\project{Capstone Project}{F 2020}{Machine learning for anomaly detection on credit card purchases}\\ % CV-ONLY
\project{Class Project}{F 2020}{Algae bloom detection with Random Forest}\\ % CV-ONLY
\project{Honors Presentation}{F 2020}{Isolation Forest with an engineering application}\\ % CV-ONLY


\section{Leadership Experience} % CV-ONLY
 % CV-ONLY
\resumeSubheading{Financial Officer}{The 4th Paradigm (CSU Data Science Club)}{August 2018 - May 2021}{Fort Collins, CO}{ % CV-ONLY
\begin{itemize} % CV-ONLY
	\item Served on the leadership committee, which directed club vision and goals % CV-ONLY
	\item Planned club events, purchased refreshments and materials for club events % CV-ONLY
	\item Solicited and secured funding from sources within and beyond the university % CV-ONLY
	\item Managed all official financial documentation and disbursement for club events % CV-ONLY
\end{itemize} % CV-ONLY
} % CV-ONLY



\section{Awards}  % CV-ONLY
 % CV-ONLY
\award{Maurice Davies Award}{CSU Statistics Department}{May 2022}{ % CV-ONLY
	The CSU Statistics department's most prestigious undergraduate award. More information can be found here: https://statistics.colostate.edu/maurice-davies-award/ % CV-ONLY
} % CV-ONLY
 % CV-ONLY
\award{Dean's List}{CSU College of Natural Sciences}{May 2018, May 2019, May 2021, May 2022}{ % CV-ONLY
	Member of the CSU Dean's List for every academic year of enrollment. % CV-ONLY
} % CV-ONLY
 % CV-ONLY
\award{Robert Zoellner Philosophy Undergraduate Scholarship}{CSU Philosophy Department}{May 2020, May 2021}{ % CV-ONLY
	Awarded to a full-time or part-time undergraduate student majoring in Philosophy, with good academic standing. % CV-ONLY
} % CV-ONLY
 % CV-ONLY
\award{Early Undergraduate Achievement Award}{CSU Statistics Department}{May 2022}{ % CV-ONLY
	This award is given to a promising student early in their academic career. % CV-ONLY
} % CV-ONLY
 % CV-ONLY
\award{University Honors Scholar}{CSU Statistics Department}{August 2018}{ % CV-ONLY
	Member of the Colorado State University Honors Program. % CV-ONLY
} % CV-ONLY
 % CV-ONLY

\end{document}
